Real-time resolution of short-read assembly graph using ONT long reads

### 2020-11-22 Revision_1/plos_latex_edit.tex

Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover. During the traversal, a variable $d$ is updated as an estimation for the distance to the target. A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21). 
A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.

Note that the $length()$ functions for node and edge are totally different. While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges). For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.

>>>>

Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover. During the traversal, a variable $d$ is updated as an estimation for the distance to the target. A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21). 
\cancel{A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.}
\addnew{Another threshold for the maximum traversing depth is set and heuristic cut-off can be used to preven exceptional combinatorial explosion when traversing extremely complex graph components.}

\cancel{Note that the $length()$ functions for node and edge are totally different. While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges). For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.} 
\addnew{It worths noting that from the pseudo code in Algorithm~\ref{algo:findpath}, despite of identical name, procedure $length()$ used for nodes are different than for edges. The former would return the contig length while the latter measure the overlap or distance between a pair of contigs thus can be negative or positive respectively. From De Bruijin graph for instance, all edges have same the length value of $-k$. In \npgraph{}'s algorithm, an edge's length can vary as we allow additional connection types on top of the original \spades{} assembly graph input.}
